Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-09-03 paper/zhang-cook-laa-langrene-menendez.tex
update plot aesthetics

{\centering \includegraphics[width=0.7\linewidth]{/Users/ursulalaa/papers/paper-tour-vis/figs/tour-path}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/ursulalaa/papers/paper-tour-vis/figs/toy-search-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/ursulalaa/papers/paper-tour-vis/figs/toy-interp-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/ursulalaa/papers/paper-tour-vis/figs/toy-pca}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/ursulalaa/papers/paper-tour-vis/figs/toy-pca-animated-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/ursulalaa/papers/paper-tour-vis/figs/toy-tour-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/ursulalaa/papers/paper-tour-vis/figs/toy-torus-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/ursulalaa/papers/paper-tour-vis/figs/interruption-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/ursulalaa/papers/paper-tour-vis/figs/polish-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/ursulalaa/papers/paper-tour-vis/figs/noisy-better-geo-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/ursulalaa/papers/paper-tour-vis/figs/kol-result-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/ursulalaa/papers/paper-tour-vis/figs/flip-sign-1}

>>>>

{\centering \includegraphics[width=0.7\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/tour-path}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/toy-search}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/toy-interp-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/toy-pca}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/toy-pca-animated-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/toy-tour-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/toy-torus-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/interruption-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/polish-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/noisy-better-geo}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/kol-result}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/flip-sign}
